Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
more work on section 5.1

We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans. Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\Graph) \simeq F\lCsp.$$

>>>>

We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans. Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.  One can show using Theorem \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
